---
title: "trains"
author: "Ishika Ravat"
format: html
execute:
  echo: false
---

This study examines attitudes towards immigration. The key covariate of interest is exposure towards Spanish-speakers, and the outcome is measured in the average causal effect of anti-immigration attitudes. A potential weakness is that the survey may not actually measure the attitudes towards immigration, just the answers to the questions in the survey. We model anti-immigration attitudes as a linear function of exposure towards Spanish-speakers.



```{r}
#| message: false
library(tidyverse)
library(tidymodels)
library(broom)
library(gt)
library(marginaleffects)
library(primer.data)
```

```{r}
glimpse(trains)
```

```{r}
linear_reg(engine = "lm") |> fit(att_end ~ treatment + age, data = trains)
```

```{r}
#| cache: true
fit_att <- linear_reg(engine = "lm") |> fit(att_end ~ treatment, data = trains)
```

```{r}
tidy(fit_att, conf.int = TRUE)
```

```{r}
tidy(fit_att, conf.int = TRUE) %>%
  select(term, estimate, conf.low, conf.high) %>%
  mutate(across(where(is.numeric), ~ signif(.x, 3))) %>%
  gt() %>%
  tab_header(
    title = "Causal Effect of Exposure to Spanish-Speakers on Attitude Toward Immigration",
    subtitle = "Data source: trains dataset from primer.data"
  ) %>%
  cols_label(
    term = "Parameter",
    estimate = "Estimate",
    conf.low = "95% CI Lower Limit",
    conf.high = "95% CI Upper Limit"
  )
```

```{r}
predictions(fit_att)
```

```{r}
plot_predictions(fit_att, condition = "treatment", draw = FALSE) %>%
  ggplot(aes(x = treatment, y = estimate, ymin = conf.low, ymax = conf.high, color = treatment)) +
  geom_point(size = 4) +
  geom_errorbar(width = 0.2, linewidth = 1) +
  scale_color_manual(values = c("Control" = "#2c3e50", "Treated" = "#e74c3c")) +
  labs(
    title = "Immigration Attitude Score After Exposure to Spanish-Speakers",
    subtitle = "Exposure to Spanish-speakers led to a more conservative attitude score on average",
    caption = "Source: trains dataset from primer.data. Error bars show 95% confidence intervals.",
    x = "Treatment Group",
    y = "Predicted Ending Attitude Score (3 to 15)"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold", size = 16, margin = margin(b = 10)),
    plot.subtitle = element_text(face = "italic", size = 12, color = "gray30", margin = margin(b = 20)),
    plot.caption = element_text(size = 9, color = "gray50", margin = margin(t = 15)),
    legend.position = "none",
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10)),
    panel.grid.minor = element_blank()
  )
```





