---
title: "trains"
author: "Ishika Ravat"
format: html
execute:
  echo: false
---

This study examines attitudes towards immigration. The key covariate of interest is exposure towards Spanish-speakers, and the outcome is measured in the average causal effect of anti-immigration attitudes. A potential weakness is that the survey may not actually measure the attitudes towards immigration, just the answers to the questions in the survey. We model anti-immigration attitudes as a linear function of exposure towards Spanish-speakers.



```{r}
#| message: false
library(tidyverse)
library(tidymodels)
library(broom)
library(gt)
library(primer.data)
```

```{r}
glimpse(trains)
```

```{r}
linear_reg(engine = "lm") |> fit(att_end ~ treatment + age, data = trains)
```

```{r}
#| cache: true
fit_att <- linear_reg(engine = "lm") |> fit(att_end ~ treatment, data = trains)
```

```{r}
tidy(fit_att, conf.int = TRUE)
```

```{r}
tidy(fit_att, conf.int = TRUE) %>%
  select(term, estimate, conf.low, conf.high) %>%
  mutate(across(where(is.numeric), ~ signif(.x, 3))) %>%
  gt() %>%
  tab_header(
    title = "Causal Effect of Exposure to Spanish-Speakers on Attitude Toward Immigration",
    subtitle = "Data source: trains dataset from primer.data"
  ) %>%
  cols_label(
    term = "Parameter",
    estimate = "Estimate",
    conf.low = "95% CI Lower Limit",
    conf.high = "95% CI Upper Limit"
  )
```





